\systemEnding: Bootstrapping Domain-Specific Languages for Neurally-Guided Bayesian Program Learning

### 2018-06-08 short.tex
2 pages

  \end{figure}
\begin{figure}\centering
\tiny
  \begin{tabular}{lll}
\multicolumn{3}{c}{Tasks and synthesized programs:}\\
cut&F &Moss Side \\ 
control&CL &Burnage \\
  control&F & City Centre\\
cut& PCFL& Brooklands \\
    \hline
\scode{\textbackslash l*\textbackslash l} & \scode{((\textbackslash u\textbackslash u)*)\textbar F}& \scode{( \textbar\textbackslash u\textbackslash w*)*} \\
    \bottomrule
  \end{tabular}
  \quad
    \begin{tabular}{l}
\multicolumn{1}{c}{DSL:}\\
$f_1 = $ \scode{\textbackslash u\textbackslash w*}\\
$f_2(x) = $ \scode{($x$|$f_1$)*} $=$ \scode{($x$|\textbackslash u\textbackslash w*)*}\\
$f_3(x) =  f_2(\scode{space}) = $\scode{( \textbar\textbackslash u\textbackslash w*)*}\\
\hline
$f_4(x) = $ \scode{($x$*$x$)} (equivalent to regex `plus')\\
$f_5 = f_4(\scode{\textbackslash l}) = \scode{\textbackslash l*\textbackslash l}$\\
    \bottomrule
  \end{tabular}
\\
\begin{tabular}{ccc}
\multicolumn{3}{c}{samples from synthesized programs:}\\
 \scode{\textbackslash l*\textbackslash l} & \scode{((\textbackslash u\textbackslash u)*)\textbar F}& \scode{( \textbar\textbackslash u\textbackslash w*)*} \\
\hline
ya&DQDF & Vr DR \\ 
fcbadcvoaobvjf&F &BeF lKQ \\
mgs&F& W\\
piljnl& KI& kqBfZ 0 \\
    \bottomrule
  \end{tabular}
            \centering 
            \includegraphics[width=.25\textwidth]{figures/nampiregexjoshcurve.png}   
\caption{regex stuff}\label{regularExpressions}
\end{figure}

>>>>

  \end{figure}
\begin{figure}
\centering
\tiny
\tabcolsep=2pt
\vspace{0pt}
\begin{tabular}{cc}
\begin{tabular}{ccc}
\multicolumn{3}{c}{Tasks:}\\
\hline
cut&F &Moss Side \\ 
control&CL &Burnage \\
control&F & City Centre\\
cut& PCFL& Brooklands \\
\multicolumn{3}{c}{Learned generative models:}\\
\hline
\scode{\textbackslash l*\textbackslash l} & \scode{((\textbackslash
u\textbackslash u)*)\textbar F}& \scode{( \textbar\textbackslash
u\textbackslash w*)*} \\
\multicolumn{3}{c}{Samples from synthesized generative models:}\\
\hline
ya&DQDF & Vr DR \\ 
glrwfdcnc&F &BeF lKQ \\
mgs&F& W\\
piljnl& KI& kqBfZ 0 \\
kj& F& ON\\
zci& GL& Bttc \\
sxpm& F& S \\
\hline
\\
\end{tabular} 
&
\begin{tabular}{c}
\begin{tabular}{l}
\multicolumn{1}{c}{Learned DSL:}\\
\hline
$f_1() = $ \scode{\textbackslash u\textbackslash w*}\\
$f_2(x) = $ \scode{($x$|$f_1$)*} $=$ \scode{($x$|\textbackslash
u\textbackslash w*)*}\\
$f_3(x) = f_2(\scode{space}) = $\scode{( \textbar\textbackslash
u\textbackslash w*)*}\\
\hline
$f_4(x) = $ \scode{($x$*$x$)}\\
\emph{ (equivalent to regex `plus')}\\
$f_5() = f_4(\scode{\textbackslash l}) = \scode{\textbackslash
l*\textbackslash l}$\\
\hline
\end{tabular}
\\
\\
\includegraphics[width=.4\linewidth]{figures/nampiregexjoshcurve3.eps} 
\end{tabular}
\end{tabular}
\vspace{-.3cm}
\caption{regex stuff}
\end{figure}
